%% 英文摘要页



\begin{center}\heiti\sanhao\textbf{
        Abstract
    }
\end{center}

Abstract is a brief statement of the thesis without notes and comments, which should be stated in the third person with concise and accurate language in 600-800 Chinese characters and less than 700 words in foreign languages. The writing of an abstract should follow these principles:

1. Abstract should generally state out clearly the purpose, significance, problem, methods, results, main conclusion and its significance, creative achievements and new insights of the research program, and the results and conclusions should be emphasized. 

2. Abstract should be independent and self contained, which can offer the necessary information without reading the full text. It is the miniature and abbreviation of a thesis, which contains the thesis’s main points, views and conclusions in a short and clear way. Abstract is a complete short essay with data and conclusion, which can be adopted and referred to independently. 

3. Abstract should include main information of the original thesis as far as possible for the reader to determine whether to read the full text, which can also be applied for secondary sources. 
4. Abstract should be written in words without any appended drawings and photos. Unless there is no alternative way available, abstract should be presented without graphs, tables, chemical structural equations, non-public common symbols and terminology, subscripts, and other special symbols. It is the best policy to highlight the key points clearly with less data tables.

Keywords are words or terms selected from the thesis for literature indexing to represent the topic information entry. Generally, a thesis should have 3-5 keywords, which should be arranged from broad to narrow entry according to the principle of epitaxial order. EI standard retrieval words are recommended. The keywords should be separated by a comma and there is no punctuation after the last word. If possible, it is better to use the standard words from Chinese Thesauri and other dictionaries of the same type. 

Abstract should be centered in bold-3 word size. It is the primary heading without any blank line between the word “abstract” and its content. But there should be one blank line between the abstract content and the key words. The “keywords” should be in bold Song typeface with small-four word size. The content and the key words are written in Chinese song typeface, English Times New Roman, small-four word size and 1.5 spaced.\\

\textbf{KEY WORDS：} Thesis, Format, Standardization, Template

\newpage\quad %加一页，使得目录第一页的页眉为 目录
\clearpage